Stability and Chaos in Multi Agent Reinforcement Learning

### 2020-10-07 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
rollback
minor edits

We illustrate these implications in Figure \ref{fig:theory} which plots the value obtained by the right hand side of (\ref{eqn::Final}). In order to determine these values, we first had to solve (\ref{eqn::fixed_point}) for $q$ and $\chi$. We determine the $\xfixed$ which solves the expression inside the square brackets of (\ref{eqn::fixed_point}) using a Newton-Raphson root-finding approach and use the following expressions for $q, \chi$ to determine their value.

\begin{equation*}
    \begin{split}
        1 = \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z) exp(-\frac{z^2}{2}) dz \\ 
        q = \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z)^2 exp(-\frac{z^2}{2}) dz \\ 
        \chi = \frac{1}{q^{n/2}}\frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \frac{\partial \xfixed (z)}{\partial z} exp(-\frac{z^2}{2}) dz
    \end{split}
\end{equation*}

It should note that this method of finding $\xfixed$ yields only an approximate value and so the $q, \chi$ which are found are estimates of their true value.

We consider each of the implications 2-5 from the previous section in turn, choosing to forego illustrating 1 as it can be seen trivially from the expression. In those heatmaps for which $\tau$ is held fixed \textbf{denote them}, we choose $\tau = 0.05 $ and vary $\Gamma$ in the range $[-1, 0]$ and $\alpha$ in the range $[0.01, 0.05]$. For those in which $\alpha$ is held fixed, \textbf{denote them} we choose $\alpha =  0.05$ and vary $\tau$ in the range $[0.01, 0.05]$.

By looking at the values of the heatmap, we see that, for all choices of the parameters, other than $\alpha = 0, \tau = 0$, (\ref{eqn::Final}) evaluates to a negative value, which signals instability. As such, the analysis over-estimates the region of instability. We believe that this is due to the heavy assumptions made during the derivation of the analytic result, the strongest of which was to drop the discrepancy between players and actions, treating each action of each player to be independent and identically distributed. However, even within the error that this assumption generates, it is still clear (and is verified experimentally) that convergence in Q-Learning is rare. Indeed as the choice of $N$ increases, the stability boundary determined by experiment (Figure \ref{fig:NumericalExperiments}) tends towards $\alpha = 0, \tau = 0$.

Similarly, as the value of $N$ increases, the values in the heatmap (seen on the right of the map) reduce. This is due to the assumption made in the derivation of the analytic result that $N \rightarrow \infty$. As the value of N increases, the discrepancy between the true behaviour of the system and analytic result decreases. This does, however, give rise to a limitation of the result - namely that the effect of the number of actions $N$ cannot be accurately inferred from the (\ref{eqn::Final}). However, it should still be noted that, even with the increase of N, the values in parameter space remain negative and still, accurately, predict instability. We go on to verify that the effect of $p, \alpha, \Gamma$ and $\tau$ are accurately captured by (\ref{eqn::Final}).

@@

>>>>

We illustrate these implications \fb{which implications? we might need a some more introductory beginning.} in Figure \ref{fig:theory}
which plots the value obtained by the right hand side of
(\ref{eqn::Final}). In order to determine these values, we first had
to solve (\ref{eqn::fixed_point}) for $q$ and $\chi$. We determine the
$\xfixed$ which solves the expression inside the square brackets of
(\ref{eqn::fixed_point}) using a Newton-Raphson root-finding approach
and use the following expressions for $q, \chi$ to determine their
value.

\begin{eqnarray*}
%    \begin{split}
        1 & = & \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z) exp(-\frac{z^2}{2}) dz \\ 
        q & = & \frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \xfixed(z)^2 exp(-\frac{z^2}{2}) dz \\ 
        \chi & = & \frac{1}{q^{n/2}}\frac{1}{\sqrt{2 \pi}} \int_{-\infty}^{\infty} \frac{\partial \xfixed (z)}{\partial z} exp(-\frac{z^2}{2}) dz
%    \end{split}
\end{eqnarray*}

It should be noted that this method of finding $\xfixed$ yields only
an approximate value and so the $q, \chi$ which are found are
estimates of their true value.

@@

\subsection{Evaluating the Stability Analysis}

\fb{I would restructure this section so that each point (2)-(5) is treated individually.}

We consider each of the implications (2)-(5) from the previous section
in turn, choosing to forego illustrating (1) as it can be seen immediately
from the expression. In those heatmaps where $\tau$ is held fixed
\textbf{denote them}, we choose $\tau = 0.05 $ and vary $\Gamma$ in
the range $[-1, 0]$ and $\alpha$ in the range $[0.01, 0.05]$. For
those in which $\alpha$ is held fixed, \textbf{denote them} we choose
$\alpha = 0.05$ and vary $\tau$ in the range $[0.01, 0.05]$.

By looking at the values of the heatmap, we see that, for all choices
of the parameters, other than $\alpha = 0, \tau = 0$,
(\ref{eqn::Final}) evaluates to a negative value, which signals
instability. As such, the analysis over-estimates the region of
instability. We believe that this is due to the
%heavy
assumptions made during the derivation of the analytic result, the
strongest of which was to drop the discrepancy between players and
actions, treating each action of each player to be independent and
identically distributed. However, even within the error that this
assumption generates, it is still clear (and is verified
experimentally) that convergence in Q-Learning is rare. Indeed as the
value of $N$ increases, the stability boundary determined by
experiment (Figure \ref{fig:NumericalExperiments}) tends towards
$\alpha = 0, \tau = 0$.

Similarly, as the value of $N$ increases, the values in the heatmap
(seen on the right of the map) reduce. This is due to the assumption
made in the derivation of the analytic result that $N \rightarrow
\infty$. As the value of N increases, the discrepancy between the true
behaviour of the system and analytic result decreases. This does,
however, give rise to a limitation of the result - namely that the
effect of the number of actions $N$ cannot be accurately inferred from
 (\ref{eqn::Final}). However, it should still be noted that, even
with the increase of $N$, the values in parameter space remain negative
and still, accurately, predict instability. We go on to verify that
the effect of $p, \alpha, \Gamma$ and $\tau$ are accurately captured
by (\ref{eqn::Final}).
